% Glossareinträge
% \newglossaryentry{amplification}{name={Amplification}, description={describes the disproportionate increase of a response packet compared to the initial request packet.}}
\newglossaryentry{api}{name={Caruso API}, description={The Caruso interface through which vehicle data is received from the OEMs and vehicles can be registered.}}
\newglossaryentry{dataplace}{name={Caruso dataplace}, description={A digital marketplace where Caruso sells subscriptions to data items.}}
\newglossaryentry{subscription}{name={Caruso dataplace subscription}, description={A subscription to one or more data items in the Caruso dataplace.}}
\newglossaryentry{ci}{name={CI}, description={Corporate identity. The manner in which a company presents itself and its products to the public, for example logos, colours or brands.}}
\newglossaryentry{appetiser}{name={data appetiser}, description={A presentation showcasing Caruso data items.}}
\newglossaryentry{data}{name={data item}, description={A single standardised point of data sold in the Caruso dataplace.}}
\newglossaryentry{sprint}{name={design sprint}, description={A process of gathering requirements which is used iteratively in five phases to create prototypes.}}
\newglossaryentry{moscow}{name={MoSCoW method}, description={A prioritisation method for requirements. Stands for Must have, Should have Could have and Won't have.}}
\newglossaryentry{nontechnical}{name={non-technical}, description={A person who uses or otherwise interacts with Caruso data items without deeper knowledge or understanding of the technology behind them.}}
\newglossaryentry{oem}{name={OEM}, description={Original equipment manufacturer. The car manufacturers who sell the raw vehicle data to Caruso.}}
\newglossaryentry{persona}{name={persona}, description={A fictional person representative of a stakeholder in the project.}}
\newglossaryentry{stakeholder}{name={stakeholder}, description={A person, group, company or other entity who is impacted by the success of the project. Can be seperated into the core target group, direct stakeholders and indirect stakeholders.}}
\newglossaryentry{telemetry}{name={telemetry data}, description={Data that is automatically gathered and transmitted during the use of a vehicle such as position, fuel gauge or indicator lamps.}}
\newglossaryentry{usecase}{name={use case}, description={A standalone action the user wants to take with the help of the application to achieve a specific goal.}}
\newglossaryentry{userstory}{name={user story}, description={A requirement in the form \enquote{as a \emph{role} I want to \emph{action} to achieve \emph{goal}}}, plural={user stories}}
\newglossaryentry{vin}{name={VIN}, description={Vehicle identification number. A unique identifier for a vehicle. Used to register vehicles in the Caruso dataplace. Used by both technical and non-technical people.}}
\newglossaryentry{widget}{name={widget}, description={A small, standalone piece of the user interface built for a single purpose.}}