\chapter{Look and Feel Requirements}
\label{sec:lookandfeel}

\section{Look and Feel Requirements}

The following section will discuss the visual and tactile aspects of Carvis to ensure that it meets the desired standards for aesthetics and usability.
\label{sec:appearancerequirements}

\snowcard{Appearance Requirements}
{Should}
{Simple and understandable}
{Carvis should have a simple, easily understandable interface for \gls{nontechnical} users to not overwhelm them. It should feel \enquote{live}, using \glspl{data} that are as recent as possible.}
{A survey is launched which asks respondents to rate on a scale how easy the UI is to use based on looks alone.}

\snowcard{Appearance Requirements}
{Should}
{Realtime data}
{The connection between to the real world data and vehicles should be apparent. In addition, the usefulness of the \glspl{data} should be brought attention to. The user should recognise their benefit and be inspired as to how to use them.}
{A tester is able to tell, when the last update of the data was.}

\snowcard{Style Requirements}
{Could}
{Corporate indentity}
{Carvis should be visually appealing by complying with the corporate indentity (\gls{ci}) of the customer.}
{Can only be tested by getting feedback from decision makers}

\snowcard{Style Requirements}
{Could}
{Corporate indentity}
{In relation to the requirement \autoref{NFR{4}}, the UI should not only be understandable and simple, but also easy and quick to use, but still bring added value to the user.}
{A use can navigate to specific pages within 5 seconds.}
