\chapter{Risks}

% Sprint Questions
All projects involve the risk of something going wrong. While risk is an inherent part of any project, it is only a problem if it is ignored and becomes a major issue. Risk management involves identifying the risks that are most likely to affect the project, developing contingency plans in case they do become problems, and monitoring the project to give early warnings of potential risks. In this section of the specification, a list of the most likely and most serious risks for the project will be provided, along with the probability of them becoming a problem and any contingency plans in place. By effectively managing these risks, the project team can minimize their impact and ensure the success of the project.

% the selected widgets are not sufficent to cover usecases -> high rist because we did focus on only one usecase
% One potential risk for this project is the possibility of there being the wrong widgets, due to the focus on one use case and the widgets not being created in consultation with the relevant decision makers. This risk is high as it has the potential to significantly impact the overall success of the project. If the wrong widgets are developed, it could lead to delays, additional costs, and potentially even project failure. This could involve seeking input and approval from the relevant decision makers at key points in the development process, or conducting more thorough user testing to ensure that the widgets meet the needs of the target audience. By proactively addressing this risk, we can significantly reduce the likelihood of it becoming a problem and ensure the success of the project.
% -> we can ignore this risk because caruso said so (noted in the relevant facts and assumptions chapter)

% the feasibilty was not checked -> medium risk as all features where designed with the capabilities of the caruso database in mind but that is just theoretical
A potential risk for this project is that the feasibility of the widgets was not checked in practice. This risk is medium as it could have some impact on the project, but is not necessarily a showstopper. To reduce the impact of this issue, all widgets were designed with the capabilities of the Caruso dataplace in mind, specifically their datapoint catalogue. In case of any issues, the widgets can be adjusted to fit the capabilities of the Caruso dataplace or be discared.

% the configuration could not be easy to understand -> low risk as the configuration was designed in cooperation with the configurator to be easy to understand as this is the main goal of the project
There is a low risk that the configuration may not be easy to understand. To mitigate this issue, the configuration has been designed in cooperation with the configurator. This ensures that the configuration is clear and easy to follow, reducing the probability of it becoming a problem. If the configuration does happen to be confusing, a contingency plan has been put in place to provide additional support and assistance to those who may be struggling to understand it. This includes providing additional resources and guidance to help individuals navigate the configuration more effectively or even providing additional training to help them understand the configuration.

% caruso is not intending to invest their own development time in this project -> low risk critical decision maker point of views are not considered the product would not be usefull for them
Caruso may not invest their own development time in this project. While this could potentially be a problem, there is no hard requirement for a specific set of functionality, so the risk of this becoming a real issue is relatively low. However, it is important to note that this risk could only become a problem after the timeline of this project has been completed. As such, a contingency plan is not currently within the scope of this project. If Caruso does not invest their own development time in the project, it may be necessary to reassess the situation and consider potential alternative solutions or approaches.

% (maybe) the customer needs to be trained -> low risk as the data is designed to be easy to undestand as this is the main goal of the project

% (maybe) the configurator needs to be trained -> low risk as the configurator is designed in cooperation with the configurator 